\speculake: Hiding Malware in Speculative Execution

### 2018-05-03 paper/introduction.tex
intro quick pass
fixup claims in intro

However, with some effort, these existing techniques can be defeated. Analysts can use
dynamic execution to unpack malware and reveal its
behavior~\cite{balzarotti2010efficient}, and can use symbolic execution or code
coverage fuzzers to determine the inputs or triggers that will reveal malicious
behavior~\cite{moser2007exploring,schwartz2010all,wang2017angr,egele2012survey}.

@@

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and evaluate their performance.
We find that the speculative window is limited mainly by the reorder buffer
size, and confirm that we are able to execute between 100 and 200 instructions
speculatively on modern Intel CPUs. While brief, we are able to perform
execution in short steps, communicating intermediate results back to the ``real
world'' part of the payload program. Using this technique,
we demonstrate implementing a universal Turing machine
(demonstrating arbitrary computation), a custom instruction set architecture
that fits within the constraints of speculative execution, and show
the ability to perform AES decryption
of a payload via AES encrypt/decrypt instructions.

Using these building blocks, we demonstrate the practicality of hiding arbitrary
computation by decrypting an AES-encrypted ARM binary in the speculative world
one instruction at a time, returning the decrypted next instruction to the real
world part of the payload program, which updates a virtual machine. We show that
we are able to decrypt and process approximately 25 instructions per second.

@@

% TODO: we don't talk at all about how an analyst might try to enumerate
% the potential entry points to the speculative world, and how that can be
% made difficult

>>>>

However, with some effort, these existing malware techniques can be defeated.
Analysts can use
dynamic execution to unpack malware and reveal its
behavior~\cite{balzarotti2010efficient}, and can use symbolic execution or code
coverage fuzzers to determine the inputs or triggers that will reveal malicious
behavior~\cite{moser2007exploring,schwartz2010all,wang2017angr,egele2012survey}.

@@

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and evaluate their performance.
We find that the speculative window is limited by the reorder buffer
and physical register file sizes, which allows us to execute between 100 and 200 instructions
speculatively on modern Intel CPUs. While brief, we are able to perform
execution in short steps, communicating intermediate results back to the ``real
world'' part of the payload program. Using this technique,
we demonstrate implementing a universal Turing machine
(demonstrating arbitrary computation), a custom instruction set architecture
that fits within the constraints of speculative execution, and show
the ability to perform AES decryption
of a payload via AES encrypt/decrypt instructions.

Using these building blocks, we demonstrate the practicality of hiding arbitrary
computation by implementing a reverse shell in our speculative instruction set.
We show that this simple payload is able to perform several system calls
in a reasonable time, ultimately launching a dial-back TCP shell in under 8~seconds after
the trigger program starts.

%Using these building blocks, we demonstrate the practicality of hiding arbitrary
%computation by decrypting an AES-encrypted ARM binary in the speculative world
%one instruction at a time, returning the decrypted next instruction to the real
%world part of the payload program, which updates a virtual machine. We show that
%we are able to decrypt and process approximately 25 instructions per second.

@@

% Move to discussion:
% TODO: we don't talk at all about how an analyst might try to enumerate
% the potential entry points to the speculative world, and how that can be
% made difficult
